### 2023-01-04 writeups/Observations.tex
add multinomial naive bayes

\begin{center}
Table 3: Machine learning model evaluations --- binary classification
\begin{tabular}{ |c|c|c| }
\hline {\bf Model type} & {\bf Text representation} & {\bf Score}\\
\hline Decision Tree & BoW & 0.722\\
\hline Decision Tree & Frequency & 0.756\\
\hline Decision Tree & TF-IDF & 0.760\\
\hline SVM & BoW & 0.769\\
\hline SVM & Frequency & 0.757\\
\hline SVM & TF-IDF & 0.732\\
\hline Naïve Bayes & BoW & 0.638\\
\hline Naïve Bayes & Frequency & 0.591\\
\hline Naïve Bayes & TF-IDF & 0.599\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 4: Algorithm comparison --- binary classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Model type}& {\bf Score}\\
\hline Decision Tree & 0.767\\
\hline Support Vector Machine & 0.754\\
\hline Naïve Bayes & 0.600\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 5: Representation comparison --- binary classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Representation}& {\bf Score}\\
\hline Bag of Words & 0.766\\
\hline Frequency & 0.761\\
\hline TF-IDF & 0.749\\
\hline
\end{tabular}
\end{center}

Using a Friedman Chi Squared test, the \emph{p}-value for table 3 is $6.30 \times 10^{-89}$, the \emph{p}-value for the different algorithms is $1.98 \times 10^{-59}$, and the \emph{p}-value for the different representations is $1.18 \times 10^{-16}$.

\begin{center}
Table 6: Machine learning model evaluations --- type classification\\
\begin{tabular}{ |c|c|c| }
\hline {\bf Model type} & {\bf Text representation} & {\bf Score} \\
\hline Decision Tree & BoW & 0.576\\
\hline Decision Tree & Frequency & 0.567\\
\hline Decision Tree & TF-IDF & 0.555\\
\hline SVM & BoW & 0.582\\
\hline SVM & Frequency & 0.521\\
\hline SVM & TF-IDF & 0.476\\
\hline Naïve Bayes & BoW & 0.515\\
\hline Naïve Bayes & Frequency & 0.538\\
\hline Naïve Bayes & TF-IDF & 0.526\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 7: Algorithm comparison --- type classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Model type}& {\bf Score}\\
\hline Decision Tree & 0.582\\
\hline Naïve Bayes & 0.535\\
\hline Support Vector Machine & 0.524\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 8: Representation comparison --- type classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Representation}& {\bf Score}\\
\hline Frequency & 0.588\\
\hline Bag of Words & 0.585\\
\hline TF-IDF & 0.541\\
\hline
\end{tabular}
\end{center}

Using a Friedman Chi Squared test, the \emph{p}-value for table 6 is $2.52 \times 10^{-29}$, the \emph{p}-value for the different algorithms is $1.00 \times 10^{-11}$, and the \emph{p}-value for the different representations is $0.0014$.

>>>>

\begin{center}
Table 3: Machine learning model evaluations --- binary classification
\begin{tabular}{ |c|c|c| }
\hline {\bf Model type} & {\bf Text representation} & {\bf Score}\\
\hline SVM & BoW & 0.774\\
\hline SVM & Frequency & 0.760\\
\hline Decision Tree & Frequency & 0.747\\
\hline Decision Tree & TF-IDF & 0.739\\
\hline Multinomial NB & BoW & 0.732\\
\hline SVM & TF-IDF & 0.729\\
\hline Decision Tree & BoW & 0.720\\
\hline Multinomial NB & Frequency & 0.718\\
\hline Multinomial NB & TF-IDF & 0.630\\
\hline Gaussian NB & BoW & 0.630\\
\hline Gaussian NB & TF-IDF & 0.602\\
\hline Gaussian NB & Frequency & 0.600\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 4: Algorithm comparison --- binary classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Model type}& {\bf Score}\\
\hline Support Vector Machine & 0.757\\
\hline Decision Tree & 0.749\\
\hline Multinomial NB & 0.728\\
\hline Gaussian NB & 0.707\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 5: Representation comparison --- binary classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Representation}& {\bf Score}\\
\hline Bag of Words & 0.767\\
\hline TF-IDF & 0.742\\
\hline Frequency & 0.736\\
\hline
\end{tabular}
\end{center}

Using a Friedman Chi Squared test, the \emph{p}-value for table 3 is approximately 0, the \emph{p}-value for the different algorithms is $6.42 \times 10^{-33}$, and the \emph{p}-value for the different representations is $3.12 \times 10^{-29}$.

\begin{center}
Table 6: Machine learning model evaluations --- type classification\\
\begin{tabular}{ |c|c|c| }
\hline {\bf Model type} & {\bf Text representation} & {\bf Score} \\
\hline Multinomial NB & TF-IDF & 0.612\\
\hline Multinomial NB & BoW & 0.597\\
\hline SVM & BoW & 0.594\\
\hline Decision Tree & TF-IDF & 0.588\\
\hline Decision Tree & Frequency & 0.576\\
\hline SVM & Frequency & 0.556\\
\hline Decision Tree & BoW & 0.550\\
\hline Gaussian NB & BoW & 0.541\\
\hline Gaussian NB & Frequency & 0.538\\
\hline Gaussian NB & TF-IDF & 0.517\\
\hline SVM & TF-IDF & 0.509\\
\hline Multinomial NB & Frequency & 0.494\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 7: Algorithm comparison --- type classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Model type}& {\bf Score}\\
\hline Multinomial NB & 0.606\\
\hline Decision Tree & 0.585\\
\hline Gaussian NB & 0.579\\
\hline Support Vector Machine & 0.550\\
\hline
\end{tabular}
\end{center}

\begin{center}
Table 8: Representation comparison --- type classification\\
\begin{tabular}{ |c|c| }
\hline {\bf Representation}& {\bf Score}\\
\hline Bag of Words & 0.600\\
\hline TF-IDF & 0.576\\
\hline Frequency & 0.547\\
\hline
\end{tabular}
\end{center}

Using a Friedman Chi Squared test, the \emph{p}-value for table 6 is $4.29 \times 10^{-112}$, the \emph{p}-value for the different algorithms is $3.08 \times 10^{-28}$, and the \emph{p}-value for the different representations is $9.20 \times 10^{-16}$.
